\LARGE \bf Reactive Trajectory Planning and Trajectory Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-01-23 root.tex
clarifying and reducing jerk profile sectionsn

Our approach to fitting appropriate jerk profiles to complex subpaths is to further break each subpath into segments which have very simple shape.
Once this is done, each segment can be compared to a library of possible jerk profiles to find a good match.
Each segment will be defined by the vector $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
Additionally, the desired positive and negative acceleration $\mathbf{a}_m = [a^+_m , a^-_m]$ and the desired positive and negative jerk $\mathbf{j}_m = [j^+_m , j^-_m]$ for must be defined for each segment.

@@

Final forward acceleration is set to zero.
A profile with $M$ jerk phases (7 in this case) can be generated by solving for the time intervals $[\Delta t_1, ..., \Delta t_M]$.
As we show later, $\mathbf{a}_m$, and $\mathbf{j}_m$ must sometimes be modified to obtain physically possible time intervals.
To enable this, ranges of acceptable longitudinal jerk and acceleration $\mathbf{a}^{max}_m = [a^{+,max}_m , a^{-,max}_m]$ and $\mathbf{j}^{max}_m = [j^{+,max}_m , j^{-,max}_m]$ are set according to the relation in Eqs. \ref{eq:am} and \ref{eq:jm}.
In the simplest case, one value for each of the quantities expressed in these relations may be chosen for the entire path.

@@

There are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\mathbf{a}_m$ and $\mathbf{j}_m$.
We propose to define 4 other basic profiles, and our algorithm judiciously chooses the appropriate profile for every segment defined by a vector $\mathbf{b}$.
The other profiles are explained below in Section \ref{sec:jerkprofiles}.
A path is then a set of $N_s$ segments, each of which is defined by a set of parameters $\mathbf{b}_k, k = 1 ... N_s$ and can be solved individually in sequence.
Determination of where to break a path into segments is discussed below in Section \ref{sec:pathsegmentation}.

There are a total of five potential jerk profiles which have been created to cover all feasible values in $\mathbf{b}$.
All impossible scenarios are automatically ruled out (e.g., end speed above speed limit, traveling speed of zero, negative speeds in $\mathbf{b}$, etc).
It should be noted that traveling backward (i.e., in reverse gear) is not supported in this work.
To find closed-form solutions for each, a symbolic solver was used.
The target values for each profile are the time steps between jerk changes.
These are solved by plugging in $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$.

For each of the profiles, it is possible that the chosen values of $\mathbf{a}_m$ and $\mathbf{j}_m$ will not be feasible for a desired speed at the end of the phase.
This results in a negative time interval for that phase.
In many cases, modifying $\mathbf{a}_m$ and $\mathbf{j}_m$ such that they still lie within $\mathbf{a}^{max}_m$ and $\mathbf{j}^{max}_m$ will remedy this.
Specifically, jerk may be increased while peak acceleration is decreased.
This process is referred to herein as ``accel-jerk tuning''
If no acceptable values are found within the valid ranges of $\mathbf{a}^{max}_m$ and $\mathbf{j}^{max}_m$, a new jerk profile must be chosen.

To decide which profile to employ, a cascade approach is used.
Analytic values of time intervals are evaluated for each profile by plugging in values of $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ until all time intervals are positive and real.
The order in which they are attempted is: 7 $\rightarrow$ 6 $\rightarrow$ 4 / 4R $\rightarrow$ 3.

>>>>

Our approach to fitting appropriate jerk profiles to complex subpaths is to further break each subpath into segments which have very simple shape.
Once this is done, each segment can be compared to a library of possible jerk profiles to find a good match.
Each segment will be defined by the vector $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
Additionally, the desired positive and negative acceleration $\mathbf{a}_m = [a^+_m , a^-_m]$ and the desired positive and negative jerk $\mathbf{j}_m = [j^+_m , j^-_m]$ for must be defined for each segment.
A path is then a set of $N_s$ segments, each of which is defined by a set of parameters $\mathbf{b}_k$, $\mathbf{a}_{m,k}$, and $\mathbf{j}_{m,k}$ where $k = 1 ... N_s$ and can be solved individually in sequence.

@@

Final forward acceleration is set to zero.
A profile with $M$ constant jerk phases (7 in this case) can be generated by solving for the time intervals $[\Delta t_1, ..., \Delta t_M]$.
As we show later, $\mathbf{a}_m$, and $\mathbf{j}_m$ must sometimes be modified to obtain physically possible time intervals.
To enable this, ranges of acceptable longitudinal jerk and acceleration $\mathbf{a}^{max}_m = [a^{+,max}_m , a^{-,max}_m]$ and $\mathbf{j}^{max}_m = [j^{+,max}_m , j^{-,max}_m]$ are set according to the relation in Eqs. \ref{eq:am} and \ref{eq:jm}.
In the simplest case, one value for each of the quantities expressed in these relations may be chosen for the entire path.

@@

There are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\mathbf{a}_m$ and $\mathbf{j}_m$.
We propose to define 4 other basic profiles to cover all feasible values in $\mathbf{b}$., and our algorithm judiciously chooses the appropriate profile.
The other profiles are explained below.

All impossible scenarios are automatically ruled out (e.g., end speed above speed limit, traveling speed of zero, negative speeds in $\mathbf{b}$, etc).
It should be noted that traveling backward (i.e., in reverse gear) is not supported in this work.
To find closed-form solutions for $[\Delta t_1, ..., \Delta t_M]$, given $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$, a symbolic solver was used.

For each of the profiles, it is possible that the chosen values of $\mathbf{a}_m$ and $\mathbf{j}_m$ will not be feasible for a desired speed at the end of the phase.
This results in a negative time interval for one or more phases.
In many cases, modifying $\mathbf{a}_m$ and $\mathbf{j}_m$ such that they still lie within $\mathbf{a}^{max}_m$ and $\mathbf{j}^{max}_m$ will remedy this.
Specifically, jerk may be increased while peak acceleration is decreased.
This process is referred to herein as ``accel-jerk tuning''
If no acceptable values are found within the valid ranges of $\mathbf{a}^{max}_m$ and $\mathbf{j}^{max}_m$, a new jerk profile must be chosen.

To decide which profile to employ, a cascade approach is used.
Analytic values of time intervals are evaluated for each profile by plugging in new values of $\mathbf{a}_m$ and $\mathbf{j}_m$ until all time intervals are positive and real.
The order in which they are attempted is: 7 $\rightarrow$ 6 $\rightarrow$ 4 / 4R $\rightarrow$ 3.
